Pollution, agricultural productivity, and development: Evidence from coal plants in India

### 2023-02-21 presentation/slides/slides.Rmd
lots of updates!

---
title: "Pollution, agricultural productivity, and development: Evidence from coal in plants in India"
subtitle: 
author: 
  - "Joshua D. Merfeld <br> KDI School and IZA"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

@@

# Tables
plantresultstable <- readRDS("pollution_development/draft/tables/plantresultstable.rds")
pollutiontable <- readRDS("pollution_development/draft/tables/pollutiontable.rds")
yieldtable <- readRDS("pollution_development/draft/tables/yieldtable.rds")
yieldtablepm <- readRDS("pollution_development/draft/tables/yieldtablepm.rds")
yieldtabletwo <- readRDS("pollution_development/draft/tables/yieldtabletwo.rds")
yieldtablehet <- readRDS("pollution_development/draft/tables/yieldtablehet.rds")
pmeffects <- readRDS("pollution_development/draft/tables/yieldtablePM.rds")
labortable <- readRDS("pollution_development/draft/tables/labortable.rds")
labortablemonsoon <- readRDS("pollution_development/draft/tables/labortablemonsoon.rds")
labortablewinter <- readRDS("pollution_development/draft/tables/labortablewinter.rds")
labortableold <- readRDS("pollution_development/draft/tables/labortableold.rds")
ntltable <- readRDS("pollution_development/draft/tables/ntltable.rds")
yieldtableleads <- readRDS("pollution_development/draft/tables/yieldtableleads.rds")
yieldtablepostplant <- readRDS("pollution_development/draft/tables/yieldtablepostplant.rds")
laborplot <- readRDS("pollution_development/draft/tables/laborplot.rds")

@@

## Validating wind direction - particulate matter and exposure

@@

@@

## Wind direction and labor allocation, by age

```{r labortableold, include = TRUE, echo = FALSE, message = FALSE, warning = FALSE}

# Table
labortableold <- labortableold[,-1]
colnames(labortableold) <- c("all", "self", "wage", "farm", "non-farm")
kable(
      labortableold,
      align = "ccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the district level. Control variables include female, age, age squared, and (years of) education. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(c(2:6),width = "1.5cm") %>%
  row_spec(c(10), hline_after = TRUE) %>%
  row_spec(c(6,9), bold = TRUE) %>%
  kable_classic_2()

@@

## Large negative effects on older half

- Older half of sample decreases overall labor allocation
  - Driven by self-employment and nonfarm employment
- Younger half actually increases allocation!
- Consistent with health effects only on older adults, though not conclusive

@@

# Table
colnames(ntltable) <- c("(1)", "(2)")
kable(
      ntltable,
      align = "cc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:3),width = "2cm") %>%
  row_spec(c(9), hline_after = TRUE) %>%
  row_spec(c(5,8), bold = TRUE) %>%
  kable_classic_2()

>>>>

---
title: "Pollution, agricultural productivity, and development: Evidence from coal plants in India"
subtitle: 
author: 
  - "Joshua D. Merfeld <br> KDI School and IZA"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

@@

# Tables
plantresultstable <- readRDS("pollution_development/draft/tables/plantresultstable.rds")
pollutiontable <- readRDS("pollution_development/draft/tables/pollutiontable.rds")
yieldtable <- readRDS("pollution_development/draft/tables/yieldtable.rds")
yieldtablepm <- readRDS("pollution_development/draft/tables/yieldtablepm.rds")
yieldtabletwo <- readRDS("pollution_development/draft/tables/yieldtabletwo.rds")
yieldtablehet <- readRDS("pollution_development/draft/tables/yieldtablehet.rds")
pmeffects <- readRDS("pollution_development/draft/tables/yieldtablePM.rds")
labortable <- readRDS("pollution_development/draft/tables/labortable.rds")
labortablerural <- readRDS("pollution_development/draft/tables/labortablerural.rds")
labortableurban <- readRDS("pollution_development/draft/tables/labortableurban.rds")
labortableruralyoung <- readRDS("pollution_development/draft/tables/labortableruralyoung.rds")
labortableruralold <- readRDS("pollution_development/draft/tables/labortableruralold.rds")
wagestable <- readRDS("pollution_development/draft/tables/wagestable.rds")
labortablemonsoon <- readRDS("pollution_development/draft/tables/labortablemonsoon.rds")
labortablewinter <- readRDS("pollution_development/draft/tables/labortablewinter.rds")
labortableold <- readRDS("pollution_development/draft/tables/labortableold.rds")
labortableoldstate <- readRDS("pollution_development/draft/tables/labortableoldstate.rds")
ntltable <- readRDS("pollution_development/draft/tables/ntltable.rds")
yieldtableleads <- readRDS("pollution_development/draft/tables/yieldtableleads.rds")
yieldtablepostplant <- readRDS("pollution_development/draft/tables/yieldtablepostplant.rds")
laborplot <- readRDS("pollution_development/draft/tables/laborplot.rds")
yieldtablemonthly <- readRDS("pollution_development/draft/tables/yieldtablemonthly.rds")

@@

## Validating wind direction - particulate matter and exposure, monthly level

@@

## Agricultural productivity and pollution leads/lags

```{r yieldtableleads, include = TRUE, echo = FALSE, message = FALSE, warning = FALSE}

# Table
colnames(yieldtableleads) <- c("wind", "IV - PM (log)")
yieldtableleads[1:6,2] <- yieldtableleads[7:12,2]
yieldtableleads <- yieldtableleads[-c(7:12),]
yieldtableleads <- yieldtableleads[-c(7:10),]
rownames(yieldtableleads)[c(1,3,5)] <- c("lag", "current", "lead")
kable(
      yieldtableleads,
      align = "cc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions estimated agricultural yield (tons per hectare). * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:3),width = "2cm") %>%
  kable_classic_2()

@@

## Wind direction and labor allocation, by rural status

```{r labortablerural, include = TRUE, echo = FALSE, message = FALSE, warning = FALSE}

# Table
colnames(labortablerural) <- c("all", "all", "self", "wage", "farm", "non-farm")
colnames(labortableurban) <- c("all", "all", "self", "wage", "farm", "non-farm")

mat1 <- matrix(c("", "", "", "", "", ""), nrow = 1)
colnames(mat1) <- c("all", "all", "self", "wage", "farm", "non-farm")
rownames(mat1) <- c("rural")
mat2 <- matrix(c("", "", "", "", "", ""), nrow = 1)
colnames(mat2) <- c("all", "all", "self", "wage", "farm", "non-farm")
rownames(mat2) <- c("urban")

labortablerural2 <- rbind(mat1, labortablerural[c(1:2, 7:8),], mat2, labortableurban[-c(3:6),], labortableurban[c(3:6),])

kable(
      labortablerural2[-c(nrow(labortablerural2)-2, nrow(labortablerural2)-1, nrow(labortablerural2)),],
      align = "cccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the district level. Control variables include female, age, age squared, and (years of) education. The outcome in each regression is days worked in the previous seven days. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:7),width = "1.5cm") %>%
  kable_classic_2()

@@

## Wind direction and labor allocation, by age (rural only)

```{r labortableruralage, include = TRUE, echo = FALSE, message = FALSE, warning = FALSE}

# Table
colnames(labortableruralyoung) <- c("all", "all", "self", "wage", "farm", "non-farm")
colnames(labortableruralold) <- c("all", "all", "self", "wage", "farm", "non-farm")

mat1 <- matrix(c("", "", "", "", "", ""), nrow = 1)
colnames(mat1) <- c("all", "all", "self", "wage", "farm", "non-farm")
rownames(mat1) <- c("younger than 35")
mat2 <- matrix(c("", "", "", "", "", ""), nrow = 1)
colnames(mat2) <- c("all", "all", "self", "wage", "farm", "non-farm")
rownames(mat2) <- c("45 or older")

labortableruralyoung2 <- rbind(mat1, labortableruralyoung[c(1:2, 7:8),], mat2, labortableruralold[-c(3:6),], labortableruralold[c(3:6),])

kable(
      labortableruralyoung2[-c(nrow(labortableruralyoung2)-2, nrow(labortableruralyoung2)-1, nrow(labortableruralyoung2)),],
      align = "cccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the district level. Control variables include female, age, age squared, and (years of) education. The outcome in each regression is days worked in the previous seven days. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:7),width = "1.5cm") %>%
  kable_classic_2()

## One last check

- Farm labor most common in July 
- Have monthly values of wind and pollution...
  - Heterogeneity by month of the season?
  - Monsoon season only

## Heterogeneity by month of the monsoon season

```{r yieldtablemonthly, include = TRUE, echo = FALSE, message = FALSE, warning = FALSE}

# Table
colnames(yieldtablemonthly) <- c("(1)", "(2)")

kable(
      yieldtablemonthly[c(1:10, nrow(yieldtablemonthly)),],
      align = "cc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions estimated agricultural yield (tons per hectare). * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:3),width = "1.5cm") %>%
  kable_classic_2()

@@

# Table
ntltable <- ntltable[,c(1,3)]
colnames(ntltable) <- c("(1)", "(2)")
kable(
      ntltable,
      align = "cc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:3),width = "2cm") %>%
  row_spec(c(9), hline_after = TRUE) %>%
  row_spec(c(5,8), bold = TRUE) %>%
  kable_classic_2()
